### 2025-07-10 CV2/papers.tex
new papers

@@

\textbf{\href{https://arxiv.org/abs/2503.12645}{Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}} (Dmitry Kovalev). \textit{arXiv preprint arXiv:2503.12645}, 2025.

@@

\textbf{\href{https://arxiv.org/abs/2411.14601}{On Linear Convergence in Smooth Convex-Concave Bilinearly-Coupled Saddle-Point Optimization: Lower Bounds and Optimal Algorithms}} (Dmitry Kovalev, Ekaterina Borodich). \textit{arXiv preprint arXiv:2411.14601}, 2024.

@@

\textbf{\href{https://arxiv.org/abs/2212.14439}{An optimal algorithm for strongly convex min-min optimization}} (Alexander Gasnikov, Dmitry Kovalev, Grigory Malinovsky). \textit{arXiv preprint arXiv:2212.14439}, 2022.

>>>>

\textbf{\href{https://arxiv.org/abs/2411.14601}{On Linear Convergence in Smooth Convex-Concave Bilinearly-Coupled Saddle-Point Optimization: Lower Bounds and Optimal Algorithms}} (Ekaterina Borodich, Dmitry Kovalev). \textit{International Conference on Machine Learning}, 2025.
\textbf{\href{https://arxiv.org/abs/2212.14439}{An Optimal Algorithm for Strongly Convex Min-Min Optimization}} (Dmitry Kovalev, Alexander Gasnikov, Grigory Malinovsky). \textit{Uncertainty in Artificial Intelligence}, 2025.

@@

\textbf{\href{https://arxiv.org/abs/2506.23803}{SGD with Adaptive Preconditioning: Unified Analysis and Momentum Acceleration}} (Dmitry Kovalev). \textit{arXiv preprint arXiv:2506.23803}, 2025.
\textbf{\href{https://arxiv.org/abs/2503.12645}{Understanding gradient orthogonalization for deep learning via non-euclidean trust-region optimization}} (Dmitry Kovalev). \textit{arXiv preprint arXiv:2503.12645}, 2025.

@@

@@
